Electric polarizability as the fundamental variable in the dielectric properties of two-dimensional materials

### 2018-12-16 SI.tex
Add figures for paper and SI

%\usepackage{xr}
%\externaldocument{paper_v112818}

\usepackage{xr-hyper} 
%\usepackage{xr}
\externaldocument{paper_v120918fundamental}

@@

\begin{figure}[htbp]
  \centering
 \includegraphics[width=0.9\linewidth]{img/Fig-G0W0.pdf}
  \caption{Variation of $\varepsilon^{\parallel}_{\mathrm{SL}}$ and
$\varepsilon^{\perp}_{\mathrm{SL}}$ as a function of $L$ for monolayer BN 
calculated at the level of PBE and G$_{\rm 0}$W$_{0}$.  
}
  \label{fig:S1}
\end{figure}

\begin{figure}[htbp]
  \centering
 \includegraphics[width=0.9\linewidth]{img/Fig-GW-frequency.pdf}
  \caption{Dependence of Im $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega)$ and
Re $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega)$ on $L$ for monolayer BN calculated using 
many-body G$_{\rm 0}$W$_{0}$ technique. The same {\bf k}-sampling is used in all simulations 
with the only variable quantity being $L$. The systematic shift 
}
  \label{fig:S2}
\end{figure}

\begin{figure}[htbp]
  \centering
 %\includegraphics[width=0.9\linewidth]{img/Fig-GW-frequency.pdf}
  \caption{Similar as in Fig. \ref{fig:S2} but taking into account electron-hole interactions at the level of 
  the Bethe-Salpeter equation (G$_{\rm 0}$W$_{0}$ - BSE). 
  The shift in energies are reduced in comparison with G$_{\rm 0}$W$_{0}$, HSE06 and PBE but still present. 
  The magnitudes of Re $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega \to 0)$ varies inherently with $L$.  
}
  \label{fig:S3}
\end{figure}

@@

\clearpage{}
\section*{}
\label{sec:ref}
\bibliography{ref1}

>>>>

\usepackage{xr-hyper} 
%\usepackage{xr}
\externaldocument{paper}

@@

\begin{figure}[htbp]
  \centering
 \includegraphics[width=0.9\linewidth]{img/SI-GW-alpha-zero.pdf}
  \caption{Variation of $\varepsilon^{\parallel}_{\mathrm{SL}}$ and
$\varepsilon^{\perp}_{\mathrm{SL}}$ as a function of $L$ for monolayer BN 
calculated at the level of PBE and G$_{\rm 0}$W$_{0}$.  
}
  \label{fig:GW-PBE-alpha}
\end{figure}

\begin{figure}[htbp]
  \centering
 \includegraphics[width=0.9\linewidth]{img/SI-PBE-omega-in_plane.pdf}
  \caption{Dependence of Im $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega)$ and
Re $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega)$ on $L$ for monolayer BN calculated using 
many-body G$_{\rm 0}$W$_{0}$ technique. The same {\bf k}-sampling is used in all simulations 
with the only variable quantity being $L$. The systematic shift 
}
  \label{fig:GW-omega-in}
\end{figure}

\begin{figure}[htbp]
  \centering
 \includegraphics[width=0.9\linewidth]{img/SI-PBE-omega-out_of_plane.pdf}
  \caption{Dependence of Im $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega)$ and
Re $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega)$ on $L$ for monolayer BN calculated using 
many-body G$_{\rm 0}$W$_{0}$ technique. The same {\bf k}-sampling is used in all simulations 
with the only variable quantity being $L$. The systematic shift 
}
  \label{fig:GW-omega-out}
\end{figure}

\begin{figure}[htbp]
  \centering
 \includegraphics[width=0.9\linewidth]{img/SI-GW-omega-in_plane.pdf}
  \caption{Dependence of Im $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega)$ and
Re $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega)$ on $L$ for monolayer BN calculated using 
many-body G$_{\rm 0}$W$_{0}$ technique. The same {\bf k}-sampling is used in all simulations 
with the only variable quantity being $L$. The systematic shift 
}
  \label{fig:GW-omega-in}
\end{figure}

\begin{figure}[htbp]
  \centering
 \includegraphics[width=0.9\linewidth]{img/SI-GW-omega-out_of_plane.pdf}
  \caption{Dependence of Im $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega)$ and
Re $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega)$ on $L$ for monolayer BN calculated using 
many-body G$_{\rm 0}$W$_{0}$ technique. The same {\bf k}-sampling is used in all simulations 
with the only variable quantity being $L$. The systematic shift 
}
  \label{fig:GW-omega-out}
\end{figure}

\begin{figure}[htbp]
  \centering
 \includegraphics[width=0.9\linewidth]{img/SI-BSE-in_plane.pdf}
  \caption{Similar as in Fig. \ref{fig:S2} but taking into account electron-hole interactions at the level of 
  the Bethe-Salpeter equation (G$_{\rm 0}$W$_{0}$ - BSE). 
  The shift in energies are reduced in comparison with G$_{\rm 0}$W$_{0}$, HSE06 and PBE but still present. 
  The magnitudes of Re $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega \to 0)$ varies inherently with $L$.  
}
  \label{fig:BSE-omega-in}
\end{figure}

\begin{figure}[htbp]
  \centering
 \includegraphics[width=0.9\linewidth]{img/SI-BSE-out_of_plane.pdf}
  \caption{Similar as in Fig. \ref{fig:S2} but taking into account electron-hole interactions at the level of 
  the Bethe-Salpeter equation (G$_{\rm 0}$W$_{0}$ - BSE). 
  The shift in energies are reduced in comparison with G$_{\rm 0}$W$_{0}$, HSE06 and PBE but still present. 
  The magnitudes of Re $\varepsilon^{\parallel,\perp}_{\mathrm{SL}}(\omega \to 0)$ varies inherently with $L$.  
}
  \label{fig:BSE-omega-out}
\end{figure}

@@

\clearpage{}
\section*{}
\label{sec:ref}
\bibliography{ref}
